Prag Bat Summary

### 2020-10-30 analysis/summary.Rmd
add cfa reli
add local save and blueprint for RMTS

fit_2 <- cfa(model_2, data=lavaan_data_2, std.lv = TRUE)

summary(fit_2, ci = T)

semPaths(fit_2, "std")

fitmeasures(fit_2)
```

@@

summary(bfit_rel_1, ci = T)
```

>>>>

fit_2 <- sem(model_2, data=lavaan_data_2)

summary(fit_2,  standardized = T)

fitmeasures(fit_2, c("cfi", "rmsea"))

semPaths(fit_2, what = "paths", whatLabels= "stand", rotation = 1)

### compare models

model_2_2 <- '
pragmatic  =~ ad_hoc_implicature  + mutual_exclusivity + simple_inf + discourse_continuity + card_sorting
'

fit_2_2 <- sem(model_2_2, data=lavaan_data_2)

summary(fit_2_2,  standardized = T)

fitmeasures(fit_2_2, c("cfi", "rmsea"))

anova(fit_2,fit_2_2)

@@

summary(bfit_rel_1, ci = T)

semPaths(bfit_rel_1, "std")
```
